Exploring the Pareto front of multi-objective COVID-19 mitigation policies using reinforcement learning

### 2023-02-09 paper/main.tex
update pcn robustness section, table

The dataset of trajectories that PCN is trained on is pruned over time to keep only the most relevant trajectories. The returns of these trajectories are used in Figure~\ref{fig:pareto-front} to show the discovered coverage set. Each of these returns can be used as desired return for policy execution. We now assess the robustness of the executed policies, by comparing the averaged return obtained over multiple policy executions with the corresponding target return. We show that the executed policies reliably obtain returns that are similar to the desired return used to condition PCN.

Results are shown in Table~\ref{tab:pcn-robustness}. The $I_\varepsilon$ indicators shows that, over all policies, the decision maker will lose at worst $0.046$ and $0.068$ normalized returns in any of the objectives for the ODE, Binomial versions respectively. On average, it will lose $0.007$, $0.024$ normalized returns respectively, which corresponds to either a total of $3633, 1059$ more hospitalizations than expected or a total of $262, 76$ less contacts than expected.

\begin{table}[t]
    \centering
    \setlength{\tabcolsep}{0.5em} % for the horizontal padding
    {\renewcommand{\arraystretch}{1.2}% for the vertical padding
    \input{tab_pcn-robustness}
    }
    \caption{Comparing the difference in the desired return provided to PCN and the actual return PCN obtained when executing its policy. We see that, regardless of the setting, the learned policy faithfully receives a return similar to its desired return.}
    \label{tab:pcn-robustness}
\end{table}

>>>>

\begin{table}
    \centering
    \setlength{\tabcolsep}{0.5em} % for the horizontal padding
    {\renewcommand{\arraystretch}{1.2}% for the vertical padding
    \input{tab/arh/arh_binomial_robustness}
    }
    \caption{Comparing the difference in the desired return provided to PCN and the actual return PCN obtained when executing its policy. We see that, regardless of the setting, the learned policy faithfully receives a return similar to its desired return.}
    \label{tab:pcn-robustness}
\end{table}

The dataset of trajectories that PCN is trained on is pruned over time to keep only the most relevant trajectories. The returns of these trajectories are used in Figure~\ref{fig:pf-binomal-arh-budgets} to show the discovered coverage set. Each of these returns can be used as desired return for policy execution. We now assess the robustness of the executed policies, by comparing the return obtained after executing the policy with the corresponding target return. For each run, we execute the policy $10$ times and compute the $I_\varepsilon$ and $I_{\varepsilon-mean}$ metrics with respect to the coverage set learned during the run. We show that the executed policies reliably obtain returns that are similar to the desired return used to condition PCN.

Results are shown in Table~\ref{tab:pcn-robustness}. The $I_\varepsilon$ indicators shows that, regardless of the budget, the decision maker will lose at worst a $0.050$ normalized return in any of the objectives. On average, it will lose $0.010$ returns. Moreover, we emphasize that the learned coverage set contains the non-dominated returns across the whole training procedure. Since the Binomial model is stochasticity, for multiple executions of the same policy, the executions that remains in the coverage set is the one with advantageous transitions due to this stochasticity. Thus, we expect our policy-executions to obtain slightly worse results than the target-solution selected from the coverage set. In light of this, we conclude that the policies trained by PCN are reliable and produce returns as close as possible from their chosen target.
